Theories of deliberated choice

### 2023-06-21 simple.tex
Denser
Much denser

\begin{theorem}
	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: $\forall i \in I$,
	\begin{equation}
		\left\{\begin{aligned}
			&(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) \ileadstog \phi;\\
			&\forall \histk \in (…, \ar_k, ?) \suchthat \histk \nileadstog \phi: (\histk, …, \ar_l, ?) \ileadstog \phi;\\
			&(…, \ar_l, ?, \nileadstog \phi, …, \ar_k, ?) \ileadstog \phi.
		\end{aligned}\right.
	\end{equation}
	(The first two statements are equivalent.)

	Assume that ${\allleadsto} \in C$. Then 
	$[\ar_k \nileadstost \phi \land \ar_l \nileadstost \phi]$ 
	is equivalent to: 
	\begin{equation}
		\left\{\begin{aligned}
			&\exists \histk \in (…, \ar_k, ?) \suchthat \histk \nileadsto \phi \land (\histk, …, \ar_l, ?) \ileadsto \phi;\\
			&\exists \histl \in (…, \ar_l, ?) \suchthat \histl \nileadsto \phi \land (\histl, …, \ar_k, ?) \ileadsto \phi.
		\end{aligned}\right.
	\end{equation}
\end{theorem}
\begin{proof}
	$\ar_k \nileadstost \phi$ iff $\exists \histk \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi$.
\end{proof}
\begin{remark}
	Idea.
	That consequence is unfalsifiable so we cannot include anything like this in $C$ (only something stronger, but of course a stronger statement could be false). Therefore, with no addition, we are doomed that exists some situations where no claim is suitable.
\end{remark}
\begin{theorem}
	Assume that the NOT consequence holds and the claim holds.
	Prove that there is no suitable claim.
	If the claim is just the NOT cons and claim, then it is not fals.
	If the claim is weaker, it does not permit to prove that $\ar_k$ or $\ar_l$ is decisive. (BUT does it possibly prove that some arg is decisive? But it may be false.)
	If the claim is stronger, it may be false.
\end{theorem}
\begin{remark}
	Idea: then use contrapositive. Not cons implies some dec arg.
	Prove equivalence to establish that we need to assume not cons to make such claims informative (in such a way).
	We could also attempt to prove that $\exists \ar \suchthat \ar \ileadstost \phi$ but assuming the claim $C$ is everything we know, there is no hope in proving something about some argument that we ignore.

>>>>

\begin{theorem}
	Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the claim $C = \forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
\forall \hist \in (…, \ar_1, ?) \nileadstog p: (\hist, …, \ar_2, ?) \ileadstog p$.

	Assume that ${\allleadsto} \in C$. Then 
	$[\ar_k \nileadstost p \land \ar_l \nileadstost p]$ 
	is equivalent to: 
	\begin{equation}
		\forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:
		\exists \hist \in (…, \ar_1, ?) \nileadsto p \suchthat (\hist, …, \ar_2, ?) \ileadsto p.
	\end{equation}
\end{theorem}
\begin{proof}
	$\ar_k \nileadstost p$ iff $\exists \hist \suchthat \ar_k \in \histend \land \hist \nileadsto p$.
\end{proof}
\begin{remark}
	Idea.
	That consequence is unfalsifiable so we cannot include anything like this in $C$ (only something stronger, but of course a stronger statement could be false). Therefore, with no addition, we are doomed that exists some situations where no claim is suitable.
\end{remark}
\begin{theorem}
	Assume that the NOT consequence holds and the claim holds.
	Prove that there is no suitable claim.
	If the claim is just the NOT cons and claim, then it is not fals.
	If the claim is weaker, it does not permit to prove that $\ar_k$ or $\ar_l$ is decisive. (BUT does it possibly prove that some arg is decisive? But it may be false.)
	If the claim is stronger, it may be false.
\end{theorem}
\begin{remark}
	Idea: then use contrapositive. Not cons implies some dec arg.
	Prove equivalence to establish that we need to assume not cons to make such claims informative (in such a way).
	We could also attempt to prove that $\exists \ar \suchthat \ar \ileadstost \phi$ but assuming the claim $C$ is everything we know, there is no hope in proving something about some argument that we ignore.
